Global patterns of forest autotrophic carbon fluxes

### 2020-01-17 manuscript/manuscript draft.Rmd
minor editing (HM comments)

bbl: here or in the discussion, note that this is a fairly stringent test: it's easy for sub-fluxes not to sum up! (Extensive citations from EC literature for example.)

```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots 1 - 3 show two component fluxes; a larger flux, defined as the combination of the two component fluxes; and a modelled estimate of the sum of the two component fluxes. 95\\% confidence intervals are plotted for the larger flux. Plot 4 shows three belowground fluxes, and a modelled estimate of the total belowground carbon flux", fig.pos='H'}

>>>>

bbl: here or in the discussion, note that this is a fairly stringent test: it's easy for sub-fluxes not to sum up! (Extensive citations from EC literature for example.). HML: yes and no. confidence intervals are pretty large.

```{r echo=FALSE, out.width='100%', fig.cap = "Latitudinal trends in forest autotropic carbon flux. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Each panel shows major C fluxes together with component fluxes. Also plotted are predicted trends in the major C fluxes based on the sum of component fluxes. 95\\% confidence intervals are plotted for the major flux for comparison with predicted trends. In (d),  which shows three belowground fluxes, the major flux, total belowground carbon flux, is one for which we have no data", fig.pos='H'}
